---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fastPLS

<!-- badges: start -->
`r badger::badge_cran_release(pkg = "fastPLS", color = "green")`
`r badger::badge_devel("gdurif/fastPLS", color="blue")`
`r badger::badge_lifecycle("experimental", "orange")`
<!-- badges: end -->

> **WORK IN PROGRESS**

Methods for regression and classification based on Partial Least 
Squares (PLS) framework. Efficient, fast and scalable implementation 
in C++. Standard and various sparse versions of PLS approach are available.

## Installation

<!--
You can install the development verion of fastPLS with:

```r
devtools::install_github("gdurif/fastPLS")
```
-->

<!--
You can install the released version of fastPLS from [CRAN](https://CRAN.R-project.org) with:

```r
install.packages("fastPLS")
```
-->

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(fastPLS)
## basic example code
# available soon
```

